---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## HDLPrepro: Reproducing Adamek, Smeekes, Wilms (2023)

This R package contains code and datasets to reproduce the
    simulations and applications in Adamek, Smeekes, Wilms (2023) Local
    Projection Inference in High-Dimensions.
    
## Installation
This package can be installed with the devtools package:
``` {r install-devtools, eval = FALSE}
utils::install.packages("devtools")
```
You can then install the HDLPrepro package from the GitHub depository directly by running:
```{r install-github, eval = FALSE}
devtools::install_github("RobertAdamek/HDLPrepro")
```
Note that as the package contains C++ code, installing the package from source might require some additional tools depending on your system; see the details for [Windows](https://cran.r-project.org/bin/windows/Rtools/) and [Mac](https://mac.r-project.org/tools/).

This package also makes heavy use of our package `desla`, which is available on CRAN. Alternatively, the latest version of this package can be installed from the GitHub depository by running
```{r install-github-desla, eval = FALSE}
devtools::install_github("RobertAdamek/desla")
```
## Usage
In addition to a collection of functions and datasets, this package contains a several R scripts which reproduce different parts of our paper. These scripts can be found in the `inst/replication_scripts` folder of the package. They are easily accessible from the GitHub page https://github.com/RobertAdamek/HDLPrepro, or by unpacking the package tarball with `untar()`. 

These scripts make use of several packages other than `HDLPrepro` and `desla`. For completeness, we list all used packages here, as well as the package versions with which we ran the code ourselves:

- `desla` (0.2.0)
- `dplyr` (1.1.2)
- `ggpattern` (1.0.1)
- `ggplot2` (3.4.2)
- `ggpubr` (0.6.0)
- `HDLPrepro` (1.0.0)
- `readxl` (1.4.3)
- `reshape2` (1.4.4)
- `xtable` (1.8-4)

We expect these packages to remain backwards compatible, and the most up-to-date versions can be installed with
```{r install-other-packages, eval = FALSE}
utils::install.packages(pkgs = c("dplyr", "ggpattern", "ggplot2", "ggpubr", "readxl", "reshape2"))
```
Alternatively, it is possible to install the versions used in this replication package using the `remotes` package. For example, to install `ggpattern` v1.0.1, use
```{r install-remotes, eval = FALSE}
remotes::install_version("ggpattern", version = "1.0.1", repos = "https://cloud.r-project.org")
```

We also plan to maintain this package to be compatible with future versions of R, but if this is not the case, we ran all applications and simulations on R version 4.3.1 (2023-06-16 ucrt) -- "Beagle Scouts". Past versions of R can be obtained from https://cran.r-project.org/.

The scripts included are as follows:

- Simulations in Section 3.1: *Sparse Structural VAR Model*
  - `running_simulation3_1.R`: Runs the simulation and saves intermediate files in a user-chosen folder.
  - `plotting_simulation3_1.R`: Processes these files and generates the plots in our paper. 
- Simulations in Section 3.2: *Empirically Calibrated Dynamic Factor Model*
  - `processing_FREDMD.R`: Processes the data obtained from the FRED-MD database. It includes our data transformations which differ from the "default" choices, and our classification of "fast" and "slow" variables.
  - `calibrating_DFM3_2.R`: Uses the processed FRED-MD data to estimate dynamic factor models and compute their implied true impulse response functions.
  - `running_simulation3_2.R``: Uses the estimated DFMs to simulate data and estimate the impulse responses. Saves intermediate files in a user-chosen folder.
  - `plotting_simulation3_2.R`: Processes the simulation files and generates the plots in our paper.
- Application in Section 4.1: *Impulse Responses to a Shock in Monetary Policy*
  - `application4_1.R`: Estimates the models and plots the results, using the same FRED-MD processed data as that used in Section 3.2.
- Application in Section 4.2: *Impulse Responses to a Shock in Government Spending*
  - `processing_R&Z_data.R`: Processes the data obtained from the website of Valerie A. Ramey, relating to the paper Ramey and Zubairy (2018). 
  - `application4_2.R`: Estimates the models and plots the results.
  
## References
Adamek, R., S. Smeekes, and I. Wilms (2023). Local Projection inference in High Dimensions. *The Econometrics Journal*, Forthcoming. 

McCracken, M. W. and S. Ng (2016a). FRED-MD: a monthly database for macroeconomic research. *Journal of Business & Economic Statistics 34*, 574–589.

Ramey, V. A. and S. Zubairy (2018). Government spending multipliers in good times and in bad: evidence from US historical data. *Journal of Political Economy 126*, 850–901